Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-02-17 article/Article.tex
quelques typos dans le doc

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann$^{1,2}$ {\small{and}} David Legland$^{3,4,5}$}

\authoraddress{\small{
{$^1$}INRA, UMR 1198 Biologie du D\'eveloppement et Reproduction, Jouy-en-Josas, F-78350, France\\
{$^2$}ENVA, UMR 1198 Biologie du D\'eveloppement et Reproduction, Jouy-en-Josas, F-78350, France\\
{$^3$}INRA, UMR 0782 G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France\\
{$^4$}AgroParisTech, UMR 0782 G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France\\
{$^5$}INRA, UMR 1318 Institut Jean-Pierre Bourgin, Versailles, F-78026, France
}}

@@

\section{Principles}
\subsection{Crofton formula}

@@

\begin{table}[!htb]
\begin{center}\begin{tabular}{ccccccc}
shape	& $(\varphi,\theta)$ & $S$ 	& $S_{crofton}^3$ & $S_{crofton}^{13}$ & $S_{isosurface}$ \tabularnewline \hline 
ball 		& $n.a.$  		& 	$11309.8$	& $11312.0$ 	& $11306.6$ 	& $12253.9$ 	\tabularnewline 
prolate	& $( 0,  0)$  	& 	$3082.9$ 	& $2938.7$ 	& $3084.6$ 	& $3344.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $3137.3$ 	& $3086.3$ 	& $3340.6$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $3150.6$ 	& $3083.3$ 	& $3337.8$ 	\tabularnewline
oblate 	& $( 0,  0)$  	& 	$6856.8$ 	& $6290.7$ 	& $6807.6$ 	& $7387.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $6872.0$ 	& $6789.0$ 	& $7346.2$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $7154.7$ 	& $6808.5$ 	& $7366.1$ 	\tabularnewline
torus 		& $( 0,  0)$  	& 	$11843.5$	& $11417.3$ 	& $11792.9$ 	& $12785.4$ 	\tabularnewline
-			& $(45,  0)$  	& 	$-$    	& $11809.3$ 	& $11766.8$ 	& $12844.4$ 	\tabularnewline
- 			& $(45, 45)$ 	& 	$-$ 	 	& $12086.0$ 	& $11822.4$ 	& $12798.4$ 	\tabularnewline
\end{tabular}\end{center}
\caption{ \label{tab:CompareSurfaceArea}
Differences between actual surface area and its measures with different methods, 
on shapes with various orientations.
The orientation is given by the direction of the shape rotation axis, defined by 
the azimut $\varphi$ (between 0 and 360 degrees) and the colatitude $\theta$ (between 0 and 180 degrees).}
\end{table}

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann$^{1,2}$ {\small{and}} David Legland$^{3,4}$}

\authoraddress{\small{
{$^1$}INRA, UMR 1198 Biologie du D\'eveloppement et Reproduction, Jouy-en-Josas, F-78350, France\\
{$^2$}ENVA, UMR 1198 Biologie du D\'eveloppement et Reproduction, Jouy-en-Josas, F-78350, France\\
{$^3$}INRA, UMR 0782 G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France\\
{$^4$}AgroParisTech, UMR 0782 G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France\\
}}

@@

\section{Principles}
\subsection{Surface area and perimeter estimation}

@@

\begin{table}[!htb]
\begin{center}\begin{tabular}{ccccccc}
shape	& $(\varphi,\theta)$ & $S$ 	& $S_{crofton^3}$ & $S_{crofton^{13}}$ & $S_{isosurface}$ \tabularnewline \hline 
ball 		& $n.a.$  		& 	$11309.8$	& $11312.0$ 	& $11306.6$ 	& $12253.9$ 	\tabularnewline 
prolate	& $( 0,  0)$  	& 	$3082.9$ 	& $2938.7$ 	& $3084.6$ 	& $3344.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $3137.3$ 	& $3086.3$ 	& $3340.6$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $3150.6$ 	& $3083.3$ 	& $3337.8$ 	\tabularnewline
oblate 	& $( 0,  0)$  	& 	$6856.8$ 	& $6290.7$ 	& $6807.6$ 	& $7387.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $6872.0$ 	& $6789.0$ 	& $7346.2$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $7154.7$ 	& $6808.5$ 	& $7366.1$ 	\tabularnewline
torus 		& $( 0,  0)$  	& 	$11843.5$	& $11417.3$ 	& $11792.9$ 	& $12785.4$ 	\tabularnewline
-			& $(45,  0)$  	& 	$-$    	& $11809.3$ 	& $11766.8$ 	& $12844.4$ 	\tabularnewline
- 			& $(45, 45)$ 	& 	$-$ 	 	& $12086.0$ 	& $11822.4$ 	& $12798.4$ 	\tabularnewline
\end{tabular}\end{center}
\caption{ \label{tab:CompareSurfaceArea}
Differences between actual surface area and its measures with different methods, 
on shapes with various orientations.
The orientation is given by the direction of the shape rotation axis, defined by 
the azimut $\varphi$ (between 0 and 360 degrees) and the colatitude $\theta$ (between 0 and 180 degrees).}
\end{table}
